Misexpression of germline programs with loss of the X-linked intellectual disability factor KDM5C

### 2024-05-20 submission/manuscript.Rmd
update figure outlines

**Figure 4: Loss of KDM5C's catalytic activity impairs DNAme placement and long-term silencing of germline genes**
	A) KDM5C binding in EpiLCs vs PNCs - number of peaks and percentage of bound genomic regions
	B) KDM5C binding in Epilcs vs pncs germline genes - GO 
	C) Left - bar graph of germline DEGs KDM5C is bound to in EpiLCs Right - Example bigwigs
		* Brain and EpiLC shared, EpiLC-specific, Brain-specific, 
	D) Bigwigs of Increase in H3K4me3 in Kdm5c-KO amygdala at germline genes
	E) Increase in H3K4me2 in EpiLCs at germline genes (left - bigwigs, right average signal at germline gene TSS? Just KDM5C-bound genes?)
	* Previous studies only looked at ESCs, unknown if catalytic activity is required for long-term repression, especially since DNA methylation is placed later). 
	F) KDM5C expression ESC --> EpiLC (increasing then decreasing) Left - RNA right - protein 
	G) RNA expression of germline genes with catalytic dead rescue (Ilakkiya)
	H) DNA methylation in WT and 5CKO EpiLCs (Ilakkiya)

@@

# Discussion
* tissue-biased gene expression:
	* However unlike the gonadal-biased DEGs, many liver and muscle-biased DEGs have a known involvement in brain function. For example, the liver-biased DEG is _Apolipoprotein C-I (Apoc1)_, is important for lipoprotein metabolism but has also been shown to influence learning and memory (Figure 1E).

>>>>

**Figure 4: Loss of KDM5C's catalytic activity impairs DNAme placement and long-term silencing of germline genes**
	A) KDM5C binding in EpiLCs vs PNCs - number of peaks and percentage of bound genomic regions
	B) KDM5C binding in Epilcs vs pncs germline genes - GO 
	C) Left - bar graph of germline DEGs KDM5C is bound to in EpiLCs Right 
	D) Example bigwigs
		* Brain and EpiLC shared, EpiLC-specific, Brain-specific, 
	E) motif analysis of KDM5C-bound vs unbound genes

	--- separate into two figures
	D) Bigwigs of Increase in H3K4me3 in Kdm5c-KO amygdala at germline genes
	E) Increase in H3K4me2 in EpiLCs at germline genes (left - bigwigs, right average signal at germline gene TSS? Just KDM5C-bound genes?)
	* Previous studies only looked at ESCs, unknown if catalytic activity is required for long-term repression, especially since DNA methylation is placed later). 
	F) KDM5C expression ESC --> EpiLC (increasing then decreasing) Left - RNA right - protein 
	G) RNA expression of germline genes with catalytic dead rescue (Ilakkiya)
	H) DNA methylation in WT and 5CKO EpiLCs (Ilakkiya)

	Direct vs indirect binding motif analysis

@@

# Discussion
* tissue-biased gene expression:
	* However unlike the gonadal-biased DEGs, many liver and muscle-biased DEGs have a known involvement in brain function. For example, the liver-biased DEG is _Apolipoprotein C-I (Apoc1)_, is important for lipoprotein metabolism but has also been shown to influence learning and memory (Figure 1E).
* Otx2 is properly expressed in EpiLCs and prevents pgc identity https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6485399/
